\subsection{Social benefits}


Carpcomm is a ground station network that connects ground stations all over the world. This makes it possible for ground stations with short or rare satellite passes to get more communication time. Ground stations with broader communication time can obtain data from other satellites and provide it to the ground station in need of this information. The rules for accessing the Carpcomm space network are: for every byte of data you upload, you can download one byte of data from your satellite. This provides a give and take society, and it is important that each ground station has the opportunity to provide data to others. 

For ordinary people, it might not be easy to see the great social benefits of a ground station network. As mentioned, a ground station network will increase the number of downstream per pass. This is profitable for Norway since we have a landscape with a lot of mountains, which provides limitations on communication with satellites. With more data available, one can more easily investigate and improve different aspects of a satellite mission like the satellite launch, satellite power system and payload. This will improve the usefulness of satellite projects, such as NUTS. More data will provide greater benefits for those working with smaller satellites, like for example students. Increased knowledge is beneficial for education, and this is very useful to the society. 

When connecting to a network all the participants will benefit, in addition to getting more date to your own project other will receive more data as well. Small-scale satellite projects created by countries with limited resources will gain from joining a network of ground stations. B creating a network of ground stations one will achieve collaboration between countries, university and people. 
Sharing of recourses will give more knowledge to a wider range of people and increase the likelihood of new projects being created. 

