\subsection{Eirik}
My name is Eirik Skjeggestad Dale. I study computer technology, with specialization in intelligent systems. This means I have a good sense of general programming, and know alot about solving difficult programming problems. This specialization is not the most relevant to this village, or any village, but if any programming bugs appear I can use it to try to solve them. What I can contribute to the group  is general programming, and helping setting up the programs for the raspberry, and tuning it to the antenna system. I have also, through computer technology courses, worked on medium sized projects and hope my experience from these can help the group, specifically with writing our reports.

I chose the NUTS village because I've always been interested in space and everything that has to do with it. It's a real inspiration to know that I'm working on something that hopefully one day will be flying out in space and sending useful data back to us.

My expectations of EiT was that it seemed like formalizing things one already knew a lot, and that by extension it was quite boring and dull, with a lot of dead time where the group did nothing. That being said, I felt that the village was interesting, and I was looking forward to the project, while I also hoped that this would give me a chance to work with people from different fields and while I thought it might feel a little forced and formalized, give me a chance to improve my team-working abilities, and my conflict solving skills.