\chapter{Introduction}
\label{chap:introduction}
This report is rooted in the teamwork process the group experienced during our project in EiT. The basis of the report is group reflections done at the end of every day we spent working on the project. These logs contains descriptions of situations, the results of these, as well as reflections and eventually actions taken in response to the situation in question. Some events and exercises have also been highlighted as they helped the group improve or reflect upon their teamwork skills.

The report starts with a description of the group, and each individual group members expectations to EiT and the NUTS-project, as well as their academic background. After that we discuss the different situations and reflect around them, before we end it with a reflection on the project and teamwork process as a whole, what we learned and how both the project and the teamwork exercises lived up to our expectations.
\section{The Project group}
The project group consisted of 6 people from 5 different studies, so we had a wide variety of competence to use in the project. Since most of our group members study technology, we decided to make something physical, and not just theorize. The wide variety also means we are one of the most heterogeneous groups in the EiT-village. If you consider that a sociologist wouldn't be of much use in our project, we can say that inside this project, the group was quite heterogeneous, even though we only had engineer students and a science student in our group. 

All the group members have knowledge that will be useful in our project, and in the scope of this EiT-village we managed to use everyones competence. This was helpful for the collaboration and no one was left with the "Report responsible" task which is often a loophole for team members who are unable to use their knowledge. All the group members viewed space as something new and exciting which was a source of inspiration and motivation early in the project.
%\begin{table}
%	\begin{center}
%		\begin{tabular}{|p{4cm}|p{7cm}|}   
%			\hline      
%			\bf{Name} & \bf{Background} \\ 
%			\hline
%			Marius Ekerholt & Computer technology\\     
%			\hline
%			Eirik Skjeggestad Dale & Computer technology\\     
%			\hline
%			Hanne Thorshaug Andresen & Energy and Environmental technology\\     
%			\hline
%			Leif-Einar H. Pettersen & Electronics and Telecommunications\\     
%			\hline
%			Børge Irgens & Theoretical Physics\\     
%			\hline
%			Hallstein Skjølsvik & Electronics and digital design\\     
%			\hline
%		 \end{tabular}
%	\end{center}
%	\caption{Group members}
%	\label{tab:groupmembers}
%\end{table}

\input{./Introduction/Hallstein.tex}
\input{./Introduction/Hanne.tex}
\input{./Introduction/me.tex}
\input{./Introduction/expectations_of_eit_eirik.tex}
\input{./Introduction/borge.tex}
\input{./Introduction/leifeinar.tex}

